---
title: "Summarizing-Codes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summarizing-Codes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Using our same mock dataset, we can generate a summary of our codes using the `create_code_summary()` function. This function does several nifty things:

* Summarizes code counts and the proportion of transcripts/media objects they come

* Allows you to set a min count or proportion for the summary output

* Optionally plots the counts, proportions or both 

* Optionally allows you to use code labels instead of variable names (using the codebook generated by `clean_data()`!)

```{r setup}
library(DedooseR)
library(tibble)

# Mock excerpts that mimic a Dedoose export ----------------------------------

# Define your preferred coders ----------------------------------


# Recode if needed ----------------------------------


# Extract the cleaned and recoded data and codebook ----------------------------------

```

```{r}
# Create code summary ----------------------------------

```